Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-26 paper.tex
Updated Paper
Reduced similarity on Introduction and Conclusions.

    Bio-inspired algorithms have been very successful when used to solve complex
    optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
    their complexity increases so does the computing power required to execute them
    \cite{ontiveros2018high}. One strategy to address this processing need is to
    use distributed computing \cite{thain2005distributed}, or the resources
    available in the cloud to help find the solution
    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy gives us
    elasticity to increase (or reduce) the computing power to achieve a balance
    according to the nature of the problem.

    Most bio-inspired algorithms are traditionally designed with a sequential
    (synchronous) perspective \cite{porto2018evolutionary,back1996evolutionary},
    where each process must wait for the previous task to finish before continuing.
    Our proposal presents an algorithm in its entirety as a native solution in the
    cloud, fully distributed, where its processes are executed in parallel and
    asynchronously. We designed the algorithm as a cloud-native solution using the
    cloud available resources to divide the processing workload, among several
    computers or running the algorithm as a cloud service. This technique makes it
    easy to scale the computing power according to the complexity required by the
    problem \cite{armbrust2010view}.

@@

    The Animal Life Cycle Algorithm allows for multiple parameters'
    fine-tuning, facilitating the freedom to experiment with different
    alternatives to restart the population and solve extinction caused by
    nature's pressure, which will impact how quickly, and the quality of its
    solution found. We compared the results obtained with the use of historical
    elite projection versus other alternatives, using classic benchmark
    functions for optimization for comparison, where it showed favorable and
    promising results.

    As the complexity of problems increases, it is essential to have a
    scalable, replicable, and fault-tolerant model that uses collaborative
    techniques to work in the cloud, where multiple resources will be
    communicating asynchronously. This research has shown that it is possible
    to evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology. To further
    validate this work, we could use control or some more complex and demanding
    problem that requires calculating real numbers
    \cite{stanley2002evolving,miikkulainen2019evolving}. We implemented the
    algorithm using Docker containers.

>>>>

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. One technique to manage this
    processing power is to use distributed computing
    \cite{thain2005distributed} or the cloud available resources to help solve
    the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
    allows adaptation of the computing power according to the problem's
    complexity.

    Most frequently, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous job to finish before continuing. In this research,
    we present an algorithm built as a native cloud solution, totally
    distributed, where its processes are executed asynchronously and in
    parallel. We designed the algorithm using the cloud available resources to
    distribute the processing workload among several computers or as a service
    in the cloud. This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

@@

    The Animal Life Cycle Algorithm allows for multiple parameters'
    fine-tuning, facilitating the freedom to experiment with different
    alternatives to restart the population and solve extinction caused by
    nature's pressure, which will impact how quickly, and the quality of its
    found solution. We compared the results obtained with the use of historical
    elite projection versus other alternatives, using classic benchmark
    functions for optimization for comparison, where it showed favorable and
    promising results.

    As the nature of the challenge increases, it is indispensable to have an
    elastic, scalable, and fault-tolerant model designed with cloud
    collaboration processes, and asynchronous communication. We have proven
    that it is possible to evolve a population, using a distributed, parallel,
    and asynchronous strategy, inspired by the Genetic Algorithm (GA). To
    further validate this work, we could use some more demanding (or control)
    problem that requires calculating real numbers
    \cite{stanley2002evolving,miikkulainen2019evolving}. We implemented the
    algorithm using Docker containers.
